Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-19 paper/paper.tex
top 5 synflood rules

\noindent
\tname{} only reports a rule if the \nids\ instantiated with that rule
is able to capture the traffic passed on input. Consequently, by
construction, a rule that uses this set of options captures the
malicious traffic. Unfortunately, this rule is potentially
overspecified. Informally, the rule includes ``too specific''
characteristics of the malicious traffic and could potentially result
in false negatives. For example, in this particular case, note that
the option \CodeIn{windows: 64} is not included in the golden rule
from Figure~\ref{fig:synflood-example}.

@@

\Mar{listem 5 primeira regras neste caso}

>>>>

\noindent
\tname{} only reports a rule if the \nids\ instantiated with that rule
is able to capture the traffic passed on input. Consequently, by
construction, a rule that uses this set of options captures the
malicious traffic. Unfortunately, this rule is potentially
overspecified. Informally, the rule includes ``too specific''
characteristics of the malicious traffic and could potentially result
in false negatives. For example, in this particular case, note that
the option \CodeIn{windows: 512} is not included in the golden rule
from Figure~\ref{fig:synflood-example}.

@@

\begin{figure}[h]
  \vspace{-2ex}
  \lstinputlisting[language=C,numbers=none,frame=none,keywords={flags,threshold,window,icmp\_id,icmp\_seq}]{synflood-top5-rules.suricata}
  \vspace{-3ex}  
\end{figure}
